\chapter{User survey}\label{appendixA}

\textbf{Editor functioning}
\\

Is the Pluto editor functioning clear?

 
\begin{itemize}
\item{Yes}
\item{No}
\end{itemize}


\textbf{Editor functioning evaluation}
\\

If not, please describe what features you think are not clear and why.
\\


\textbf{First step, exercise 1}
\\

How much difficult was solving the first step of the first exercise?


\begin{itemize}
\item{very easy}
\item{easy}
\item{normal}
\item{hard}
\item{very hard}
\item{not solved}

\end{itemize}


\textbf{First step evaluation, exercise 1}
\\

If you didn't solve the first step, or you find it hard or very hard, please explain why.
\\


\textbf{Second step, exercise 1}
\\

How much difficult was solving the second step of the first exercise?


\begin{itemize}
\item{very easy}
\item{easy}
\item{normal}
\item{hard}
\item{very hard}
\item{not solved}

\end{itemize}
 

\textbf{Second step evaluation, exercise 1}
\\

If you didn't solve the second step, or you find it hard or very hard, please explain why.
\\

\textbf{Third step, exercise 1}
\\

How much difficult was solving the Third step of the first exercise?


\begin{itemize}
\item{very easy}
\item{easy}
\item{normal}
\item{hard}
\item{very hard}
\item{not solved}

\end{itemize}


\textbf{Third step evaluation, exercise 1}
\\

If you didn't solve the third step, or you find it hard or very hard, please explain why.
\\ 

\textbf{Editor interface}
\\

Define the usability of the Pluto editor interface.


\begin{itemize}
\item{easily usable}
\item{normal}
\item{hard to use}
\item{obscure}

\end{itemize}

\textbf{Editor interface evaluation}
\\

If you answer is 'hard to use' or 'obscure', please explain what features are tricky and why.
\\ 

\textbf{Code generation}
\\

Is the code generation step easy to perform?


\begin{itemize}
\item{easy}
\item{normal}
\item{hard}

\end{itemize}

\textbf{Code generation evaluation}
\\

If you answer is 'hard', please explain what is not clear to you and why.
\\ 

\textbf{Editor suggestions}
\\

Please write here any comment/suggestions to improve Pluto Editor.
\\ 

\textbf{User application functioning}
\\

Is the Pluto user application functioning clear?


\begin{itemize}
\item{Yes}
\item{No}
\end{itemize}

\textbf{User application functioning evaluation}
\\

If not, please explain what features you think are not clear.
\\ 

\textbf{First step, exercise 2}
\\

How much difficult was solving the first step of the second exercise?


\begin{itemize}
\item{very easy}
\item{easy}
\item{normal}
\item{hard}
\item{very hard}
\item{not solved}

\end{itemize}

\textbf{First step evaluation, exercise 2}
\\

If you didn't solve the first step, or you find it hard or very hard, please explain why.
\\ 

\textbf{Second step, exercise 2}
\\

How much difficult was solving the second step of the second exercise?
 

\begin{itemize}
\item{very easy}
\item{easy}
\item{normal}
\item{hard}
\item{very hard}
\item{not solved}

\end{itemize}

\textbf{Second step evaluation, exercise 2}
\\

If you didn't solve the second step, or you find it hard or very hard, please explain why.
\\ 

\textbf{Third step, exercise 2}
\\

How much difficult was solving the third step of the second exercise?


\begin{itemize}
\item{very easy}
\item{easy}
\item{normal}
\item{hard}
\item{very hard}
\item{not solved}

\end{itemize}

\textbf{Third step evaluation, exercise 2}
\\

If you didn't solve the third step, or you find it hard or very hard, please explain why.
\\ 

\textbf{Missions page}
\\

How much difficult was to use the Missions Page of the Pluto user application?


\begin{itemize}
\item{very easy}
\item{easy}
\item{normal}
\item{hard}
\item{very hard}

\end{itemize}

\textbf{Missions page evaluation}
\\

If you find it hard or very hard, please explain why.
\\ 

\textbf{Trips page}
\\

How much difficult was to use the Trips Page of the Pluto user application?


\begin{itemize}
\item{very easy}
\item{easy}
\item{normal}
\item{hard}
\item{very hard}

\end{itemize}

\textbf{Trips page evaluation}
\\

If you find it hard or very hard, please explain why.
\\ 

\textbf{Monitor page}
\\

How much difficult was to use the Monitor Page of the Pluto user application?


\begin{itemize}
\item{very easy}
\item{easy}
\item{normal}
\item{hard}
\item{very hard}

\end{itemize}

\textbf{Monitor page evaluation}
\\

If you find it hard or very hard, please explain why.
\\ 

\textbf{User application suggestions}
\\

Please write here any comment/suggestions to improve Pluto user application.
\\ 

